Should I Airbnb My Property?

### 2017-02-27 abb_Writeup.Rmd
data cleaning text

We start by removing property level observations missing price data. Plotting the distribution of the rates and rents we see that most long term weekly rentals are greater than \$200 and less than \$1,000 per week while most median nightly rates are greater than \$50 and less than \$500 per night (Figure 4). We filter the property level data accordingly.  We also filter the short term daily data to include only those observations with nightly rates between \$50 and \$500.

```{r ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='Melbourne Suburb Classifications'}

@@

<!-- Our final data filtering considers the observed revenue of the properties. For the long-term rentals the observed revenue is the weekly rate multiplied by 52 minus the number of weeks the property was on the market.  In a number of extreme cases, time on market was extremely long and the total observed revenues very low. To remove these outlying observations, we filter out any properties with less than $5,000 in revenue. -->

<!-- ```{r load_workspace2, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=FALSE} -->

<!--  load(paste0(data.path, '/analyzed/abb_objs.RData')) -->

<!--   abbr <- abb.revs[,c('bedbath', 'revenue')] -->
<!--   abbr$tenure <- 'short-term' -->
<!--   ltrr <- ltr.revs[,c('bedbath', 'revenue')] -->
<!--   ltrr$tenure <- 'long-term' -->
<!--   allr <- rbind(abbr, ltrr) -->

<!--   ggplot(allr, aes(x=revenue, fill=tenure, color=tenure)) + -->
<!--     geom_density(alpha=.5) + -->
<!--     scale_fill_manual(values=c(ltr.col, abb.col)) + -->
<!--     scale_color_manual(values=c(ltr.col, abb.col)) + -->
<!--     ggtitle('Annual Revenues by Tenure Type') + -->
<!--     xlab('Annual Revenue') + -->
<!--     scale_x_continuous(breaks=c(seq(0,60000, by=20000)), -->
<!--                        labels=c('$0', '$20,000', '$40,000', '$60,000'))+ -->
<!--     theme(legend.position='bottom', -->
<!--           legend.title = element_blank(), -->
<!--           plot.title = element_text(hjust = 0.5), -->
<!--           axis.text.y = element_blank(), -->
<!--           axis.ticks.y = element_blank(), -->
<!--           axis.title.y=element_blank()) + -->
<!--     coord_cartesian(xlim=c(0, 70000)) -->

@@

@@

@@

```{r loc.bars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='Location Maps'}

@@

<!-- ```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='Data Cleaning Summary'} -->

<!-- cc <- clean.count[,c('operation', 'abb', 'ltr')] -->
<!-- abb.count <- cumsum(c(cc$abb[1], -cc$abb[-1])) -->
<!-- ltr.count <- cumsum(c(cc$ltr[1], -cc$ltr[-1])) -->
<!-- abb.cut <- c(0, abb.count[-length(abb.count)] - abb.count[-1]) -->
<!-- abb.per <- c(0, abb.cut[-1] / abb.count[-length(abb.count)]) -->
<!-- ltr.cut <- c(0, ltr.count[-length(ltr.count)] - ltr.count[-1]) -->
<!-- ltr.per <- c(0, ltr.cut[-1] / ltr.count[-length(ltr.count)]) -->
<!-- clean.table <- data.frame(field=cc$operation, -->
<!--                           abbcount=abb.count, -->
<!--                           abbcut=abb.cut, -->
<!--                           abbper=abb.per, -->
<!--                           ltrcount=ltr.count, -->
<!--                           ltrcut=ltr.cut, -->
<!--                           ltrper=ltr.per) -->

<!-- rownames(clean.table) <- NULL -->
<!-- clean.table$field <- c('Initial Count', 'Time', 'Property Type', -->
<!--                        'Listing Type', 'Bedrooms', 'Baths', 'Bed/Bath Combo', -->
<!--                        'Rates & Rents', 'Location', 'Revenue') -->
<!-- clean.table$abbper <- 100*round(clean.table$abbper, 2) -->
<!-- clean.table$ltrper <- 100*round(clean.table$ltrper, 2) -->
<!-- names(clean.table) <- c('Filter', 'Short Term', 'Cut', '% Cut', -->
<!--                         'Long Term', 'Cut', '% Cut') -->
<!-- options(xtable.comment = FALSE) -->
<!-- print(xtable(clean.table, caption='Data Cleaning Summary\n', -->
<!--        digits=0), -->
<!--        include.rownames=FALSE, -->
<!--        caption.placement='top') -->

>>>>

After removing property level observations that are missing price data, we plot the distribution of the rates and rents.  In Figure 4 we see that most long term weekly rentals are greater than \$200 and less than \$1,000 per week while most median nightly rates are greater than \$50 and less than \$500 per night. We filter the property level data accordingly. We also filter the short term daily data to include only those observations with nightly rates between \$50 and \$500.

```{r ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='Distribution of Rates and Rents'}

@@

@@

 loc.map <- loc.map +     
   theme(axis.title.y=element_blank(),
         axis.text.y=element_blank(),
         axis.ticks.y=element_blank(),
         axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank())

@@

  str.map <- str.map +
   theme(axis.title.y=element_blank(),
         axis.text.y=element_blank(),
         axis.ticks.y=element_blank(),
         axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank())

  ltr.map <- ltr.map +
   theme(axis.title.y=element_blank(),
         axis.text.y=element_blank(),
         axis.ticks.y=element_blank(),
         axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank())

@@

```{r loc.bars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='Submarket Observation Counts'}

@@

```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='Data Cleaning Summary'}

cc <- clean.count[,c('operation', 'str', 'ltr')]
str.count <- cumsum(c(cc$str[1], -cc$str[-1]))
ltr.count <- cumsum(c(cc$ltr[1], -cc$ltr[-1]))
str.cut <- c(0, str.count[-length(str.count)] - str.count[-1])
str.per <- c(0, str.cut[-1] / str.count[-length(str.count)])
ltr.cut <- c(0, ltr.count[-length(ltr.count)] - ltr.count[-1])
ltr.per <- c(0, ltr.cut[-1] / ltr.count[-length(ltr.count)])
clean.table <- data.frame(field=cc$operation,
                          strcount=str.count,
                          strcut=str.cut,
                          strper=str.per,
                          ltrcount=ltr.count,
                          ltrcut=ltr.cut,
                          ltrper=ltr.per)

rownames(clean.table) <- NULL
clean.table$field <- c('Initial Count', 'Time', 'Property Type',
                       'Listing Type', 'Bedrooms', 'Baths', 'Bed/Bath Combo',
                       'Rates & Rents', 'Location', 'Revenue')
clean.table$strper <- 100*round(clean.table$strper, 2)
clean.table$ltrper <- 100*round(clean.table$ltrper, 2)
names(clean.table) <- c('Filter', 'Short Term', 'Cut', '% Cut',
                        'Long Term', 'Cut', '% Cut')
options(xtable.comment = FALSE)
print(xtable(clean.table, caption='Data Cleaning Summary\n',
       digits=0),
       include.rownames=FALSE,
       caption.placement='top')

<!-- Our final data filtering considers the observed gross revenue of the properties. For the long-term rentals the observed gross revenue is the weekly rate multiplied by 52 minus the number of weeks the property was on the market. In a number of extreme cases, time on market was extremely long and the total observed revenues very low. To remove these outlying observations, we filter out any properties with less than $10,000 in revenue. -->

<!--   strr <- str.data[,c('bedrooms', 'gross.revenue')] -->
<!--   strr$tenure <- 'short-term' -->
<!--   ltrr <- ltr.data[,c('bedrooms', 'gross.revenue')] -->
<!--   ltrr$tenure <- 'long-term' -->
<!--   allr <- rbind(strr, ltrr) -->

<!--   ggplot(allr, aes(x=gross.revenue, fill=tenure, color=tenure)) + -->
<!--     geom_density(alpha=.5) + -->
<!--     scale_fill_manual(values=c(ltr.col, abb.col)) + -->
<!--     scale_color_manual(values=c(ltr.col, abb.col)) + -->
<!--     ggtitle('Annual Revenues by Tenure Type') + -->
<!--     xlab('Annual Revenue') + -->
<!--     scale_x_continuous(breaks=c(seq(0,60000, by=20000)), -->
<!--                        labels=c('$0', '$20,000', '$40,000', '$60,000'))+ -->
<!--     theme(legend.position='bottom', -->
<!--           legend.title = element_blank(), -->
<!--           plot.title = element_text(hjust = 0.5), -->
<!--           axis.text.y = element_blank(), -->
<!--           axis.ticks.y = element_blank(), -->
<!--           axis.title.y=element_blank()) + -->
<!--     coord_cartesian(xlim=c(0, 70000)) -->
